#### FSRM 563 HW 8 Wenbo Ma

#### Read in Data
```{r}
yy=matrix(scan("Diabold_Li_data.txt"),ncol=19,byrow=T)
x=yy[1,2:19] ## x is the time to maturity (1 month, 2 months, etc.)
date = 19900531
y=yy[yy[,1]==date,2:19] ## term structure at 1990.05.31
```

#### Code for Quesiton 1,2,3 and 4
```{r}
##=======data====================
plot(x,y,xlab="time to maturity",ylab="interest rate")

##=======local polynomial========
library(KernSmooth)
dpill(x,y)
out.localPoly = locpoly(x,y,bandwidth=dpill(x,y))
lines(out.localPoly$x,out.localPoly$y,lty=1,col='blue')

##=======Basis Spline============
library(splines)
xx = bs(x,knots=2)
summary(lm(y~xx))
lines(x,lm(y~xx)$fit,lty=2,col='red')

##=======smoothing spline========
out.s=smooth.spline(x,y,cv=TRUE) ## ordinary Cross Validation
lines(out.s$x,out.s$y,lty=3,col='green')

##=======optimal lambda N-S curve approach===========

lam11 = 0.1975 ## optimal lambda getting from hw 7

##======== function to obtain Nelson-Siegel curve on a dense set of points
plotNScurve=function(min=1,max=120,lam=0.057,coef){
x=min+(1:1000)/1000*(max-min)  ## x is sequence of time 
zz1=(1-exp(-lam*x))/lam/x  
zz2=zz1-exp(-lam*x) ## 
y=coef[1]+coef[2]*zz1+coef[3]*zz2  ## interest rate
return(list(x=x,y=y))}

##======N-S model and plot=========================
zz1=(1-exp(-lam11*x))/lam11/x
zz2=zz1-exp(-lam11*x)
xx=cbind(zz1,zz2)
outNS1=lm(y~xx)
plotNS1=plotNScurve(min=1,max=120,lam=lam11,coef=outNS1$coef)
lines(plotNS1$x,plotNS1$y,main="N-S Curve",lty=4,col='black')
legend('bottomright',cex=1,lty=1,legend=c("local polynomial","basis spline","smoothing spline","N-S optimal lambda"),col=c("blue","red","green","black"))
```

### Comment:
- 1. The local polynomial does the worst job. It always underestimates the interest rate and has a large deviation at boundary.
- 2. The B-spline does good job for bond maturing at [1,12]; underestimates bond maturing at [15,21]; overestimates bond maturing at [24,84]
- 3. The smoothing spline traverses each data. It fits the data very well but may suffer from overfitting in general. For exmaple, the last data [120 month] is inverted and it is not usual in normal economic condition.
- 4. The N-S curve does good job for bond maturing at [1,36] and tends to underestimate the interest rate from then on.